LFQ: Online Learning of Per-flow Queuing Policies using Deep Reinforcement Learning

### 2021-03-05 paper/paper.tex
Final versions
Fix typo
Update paper.tex

\usepackage[english]{babel}
\usepackage{blindtext}
\usepackage{xcolor}

\usepackage[nomain, toc, acronym]{glossaries}
\usepackage{subfig}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{float}

@@

\cite{kim_deep_2019} use Deep Reinforcement Learning to develop an \gls{aqm} mechanism for IoT devices that works on the output queue of a switch.  \cite{bouacida_practical_2019,bisoy_design_2017} use \gls{rl} to build an \gls{aqm} algorithm for shared buffers. \cite{vucevic_reinforcement_2007} uses \gls{rl} as well and focuses specifically on cellular communications. \cite{lin_kemy_2015} use a custom optimization approach that relies on as offline greedy algorithm which finds optimal rules for an \gls{aqm} that fulfills a certain reward function. \cite{shah_sam_2016} build an \gls{aqm} mechanism which utilizes support vector machines to learn an optimal queuing policy for a shared buffer.

@@

In contrast to offline learning, online learning enables to train in deployment. This makes it possible to adapt the behavior slowly over time (over a time span of month or years), for example if new \glspl{cca} emerge. Furthermore, being able to training with real flows is more realistic than training only with simulated flows in a simulation.

@@

\section{Conlusion}

>>>>

\usepackage[english]{babel}
\usepackage{blindtext}
\usepackage{xcolor}
\usepackage[utf8]{inputenc}

\usepackage[nomain, toc, acronym]{glossaries}
\usepackage{subfig}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{float}

@@

\cite{kim_deep_2019} use Deep Reinforcement Learning to develop an \gls{aqm} mechanism for IoT devices that works on the output queue of a switch.  \cite{bouacida_practical_2019,bisoy_design_2017} use \gls{rl} to build an \gls{aqm} algorithm for shared buffers. \cite{vucevic_reinforcement_2007} uses \gls{rl} as well and focuses specifically on cellular communications. \cite{lin_kemy_2015} use a custom optimization approach that relies on an offline greedy algorithm which finds optimal rules for an \gls{aqm} that fulfills a certain reward function. \cite{shah_sam_2016} build an \gls{aqm} mechanism which utilizes support vector machines to learn an optimal queuing policy for a shared buffer.

@@

In contrast to offline learning, online learning enables to train in deployment. This makes it possible to adapt the behavior slowly over time (over a time span of months or years), for example if new \glspl{cca} emerge. Furthermore, being able to training with real flows is more realistic than training only with simulated flows in a simulation.

@@

\section{Conclusion}
